The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-06-05 paper/ms.tex

@@

\subsection{Light Curve Statistics}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation of light curves vs catalog
  TESS-band magnitude for CDIPS light curves.}  Faint stars in heavily
  crowded regions have bright neighbors which drive their light curve
  scatter below the expected noise limits.
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
	\caption{
		{\it Top.} Stellar properties of CDIPS stars with light curves in this data release.
		{\it Bottom.} Stellar properties of close CDIPS stars with light curves.
	}
	\label{fig:hrd}
\end{figure}

@@

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	2MASS \citep{skrutskie_tmass_2006},
    DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{astroquery.gaia}
  \texttt{astroquery.simbad}
  \texttt{astroquery.mast}
  \texttt{astroquery.nasaexopanetarchive}  
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TagSpaces} (CITE),
  \texttt{tesscut} (CITE)
}

>>>>

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{sector6_cluster_field_star_positions.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Celestial positions of light curves from Sector 6}
        \label{fig:lcradecsector6}
    }
\end{figure}

@@

\subsection{Light Curve Statistics}
\label{subsec:lcstatistics}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} The minimum RMS across all three
  aperture sizes was selected.  The photon and read noise are
  calculated using the updated figures from \citet{vanderspek_2018}.
  The noise from unresolved background stars is expected to be more
  important than read noise at the faint end, but is omitted from the
  plot due to model uncertainties (see \S~\ref{subsec:lcstatistics}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
	\caption{
    {\it Top.} HR diagram of CDIPS stars with light curves in this
    data release.  {\it Bottom.} HR diagram of close CDIPS stars with
    light curves. The wedge separating the pre-MS sample from the MS
    stars was discussed by \citet{zari_3d_2018}, who introduced it in
    order to avoid contamination by photometric binaries.
	}
	\label{fig:hrd}
\end{figure}

\begin{figure}[!ht]
	\gridline{\fig{pm_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{pm_scat_close_subset.png}{0.45\textwidth}{}}
	\caption{
    {\it Top.} Proper motions of CDIPS stars with light curves in this
    data release.  {\it Bottom.} Proper motions of close CDIPS stars
    with light curves. A few additional clusters are visible.
	}
	\label{fig:propermotions}
\end{figure}

The standard deviation of the light curves is plotted as a function of the 
catalog $T$-band magnitude for CDIPS light curves in 
Figure~\ref{fig:rms_vs_mag}.
Ignoring the expected noise contribution from the zodiacal and faint star 
background, the light curves generally seem to follow the model one would 
predict.
The bright end is somewhat noisier than the performance reported by SPOC 
(CITE), as well as the pipelines of 
Chelsea (CITE) and Ben (CITE), and maybe Ryan (CITE).
Simple aperture photometry should out-perform image subtraction techniques in 
the bright regime, so this is not particularly unexpected.

A few points concerning the noise model predictions are relevant.
First, the effects of crowding are not apparent in 
Figure~\ref{fig:rms_vs_mag}. 
If the reference fluxes were being measured directly from the photometric 
reference frame, the faint stars would be driven below the expected noise 
floor, because the reference fluxes would be systematically overestimated.
Our procedure for determining the reference magnitudes uses our knowledge of 
the catalog magnitudes to eliminate this effect (REFERENCE).

Second, our plot omits the noise from unresolved background stars.
If we include it, then our RMS at the faint end is about 0.7x below the model.
This suggests that the model over-predicts the background, or that we overfit 
the majority of our light curves. Both are probably a little true.

@@

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	2MASS \citep{skrutskie_tmass_2006},
    DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{astroquery.gaia}
  \texttt{astroquery.simbad}
  \texttt{astroquery.mast}
  \texttt{astroquery.nasaexopanetarchive}  
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TagSpaces} (CITE),
  \texttt{tesscut} \citep{brasseur_astrocut_2019}
}
